\documentclass{muratcan_cv}

% Define colors and icons
\definecolor{linkedinblue}{HTML}{0077B5}
\newcommand{\linkedinicon}{\faLinkedin}
\newcommand{\githubicon}{\faGithub}
\newcommand{\portfolioicon}{\faGlobe}

% Setup header information
\setname{Zaal Esartia}{}
\setaddress{Tbilisi, Georgia}
\setmobile{(+995) 599-00-00-00}
\setmail{zaal.esartia@gmail.com}

% Custom contact display command
\newcommand{\contactinfo}{%
    \begin{center}
    {\color{linkedinblue}\LARGE\textbf{\@Zaal Esartia}}\\[1ex]
    
    {\small\faPhone} \ \@597798388 \ {\small\faEnvelope} \ \href{mailto:\@email}{\@esartiazaali@gmail.com}\\
    \end{center}
}

% Social links with icons
\newcommand{\sociallinks}{%
    \href{https://www.linkedin.com/in/zaal-esartia-056bb32b2/}{\linkedinicon\hspace{0.5em}LinkedIn}
    \hspace{1em} | \hspace{1em}
    \href{https://github.com/pipki11}{\githubicon\hspace{0.5em}GitHub}
    \hspace{1em} | \hspace{1em}
    \href{https://zaalesartia.site}{\portfolioicon\hspace{0.5em}Portfolio}
}

\setthemecolor{MidnightBlue}

% Custom spacing and centering commands
\newcommand{\sectionspace}{\vspace{3ex}}
\newcommand{\subsectionspace}{\vspace{2ex}}
    
\begin{document}

% Display contact information
\contactinfo
\begin{center}
\sociallinks
\end{center}
\vspace{2ex} % more white space after header

\begin{center}
\section*{Profile}
\end{center}
{\centering
Computer Science student passionate about frontend development with hands-on experience building Angular applications. Skilled in C++, TypeScript, and modern web technologies. Looking for an internship/entry-level role to apply problem-solving and software development skills.\par}
\sectionspace

\section{Education} 
    \datedexperience{BS Computer Science}{Sep 2022 - Aug 2026}
    \explanation{
Ivane Javakhishvili Tbilisi State University}{Tbilisi, Georgia} 
    \datedexperience{High School Degree}{Sep 2010 - May 2022}
    \explanation{
Public School №35}{Tbilisi, Georgia}

% -------------------Skills -----------------

\section*{Skills}
% Define skill level command
\newcommand{\skill}[2]{%
    \textbf{#1} & #2 \\[2ex]
}

\begin{center}
\begin{tabular}{>{\color{linkedinblue}}l p{13cm}}
    \skill{Frontend Development}{
        \textbf{HTML5} • \textbf{CSS3} \hspace{1em} 
        \textbf{JavaScript} • \textbf{TypeScript} \hspace{1em}
        \textbf{Angular} \hspace{1em}
        \textbf{RxJS}
    }
    \skill{UI/UX Technologies}{
        \textbf{Sass} \hspace{1em}
        \textbf{Bootstrap} \hspace{1em}
        \textbf{Tailwind CSS}
    }
    \skill{Programming}{
        \textbf{C++} \hspace{1em}
        \textbf{System Architecture} \hspace{1em}
        \textbf{CompTIA A+} 
    }
    \skill{Development Tools}{
        \textbf{Git} \textbf{Version Control} \hspace{1em}
        \textbf{VS Code} \hspace{1em}
        \textbf{npm} \textbf{Package Manager}
    }
\end{tabular}
\end{center}
\sectionspace

\section{Projects}
    \datedexperience{\href{https://github.com/pipki11/ClipZ-Project}{ClipZ}}{December 2024}
    \explanation{Video Sharing Platform for Gamers}{Tbilisi, Georgia}
    \explanationdetail{
    \smallskip
    \coloredbullet\ %
    Developed a video-sharing platform for gamers using Angular, enabling users to upload and share gameplay clips. Built a responsive UI with Tailwind CSS, optimized performance with Angular DevTools, and implemented reusable components, directives, and a modal system for a smooth user experience.
    
    \smallskip 
    \coloredbullet\ %
    Integrated Firebase for authentication, data storage, and real-time updates, leveraging Angular services and dependency injection for scalability. Implemented form handling, validations, and all types of data binding to enhance interactivity and usability.
      
    \smallskip
    \coloredbullet\ %
    Optimized the application with Block UI and structured reusable components for maintainability. Currently refining Firebase integration and expanding features to improve performance and user engagement.
    
    \smallskip
    }

    \datedexperience{\href{https://github.com/pipki11/tech-web}{Tech-Web}}{February 2024}
    \explanation{E-commerce Platform for Apple Products}{Tbilisi, Georgia}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Built a beginner-friendly e-commerce platform using Angular, focusing on fundamental concepts such as NgModules, components, and services.
    
    \smallskip
    \coloredbullet\ %
    Implemented a dynamic product catalog showcasing 10 Apple products, with filtering options for categories like iPhones and iPads for an intuitive shopping experience.
    
    \smallskip
    \coloredbullet\ %
    Developed a fully functional cart feature, enabling users to add and remove products seamlessly while maintaining state across the application.
    
    \smallskip
    }

    \datedexperience{\href{https://github.com/pipki11/TicTacToe}{Tic-Tac-Toe}}{June 2024}
    \explanation{Interactive Browser Game}{Tbilisi, Georgia}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
 Players take turns placing their markers X or O in 3 to 3 grid, with real time updates and automatic
    
    \smallskip 
    \coloredbullet\ %
 Implemented core game logic including seamless player turns, real-time UI updates, and automatic winner detection with reset functionality.
      
     \smallskip
     \coloredbullet\ %
Showcased key Angular concepts such as component design and data binding for an engaging and educational user experience.
     
     \smallskip
     }

    

\vspace{1.5ex}
\section* {Languages}
\begin{itemize}
    \item \textbf{Georgian:} Native 
    \item \textbf{English:} B2
    \item \textbf{Russian:} Basic (A2)
\end{itemize}


\end{document}

